When are Fuzzy Extractors Possible?

### 2014-10-03 info-bounds/FuzzyExtPossibility.tex
working on techniques section

\newcommand{\expinfo}{\ensuremath{\mathcal{E}}}
\newcommand{\ext}{\ensuremath{\mathtt{ext}}}
\newcommand{\cext}{\ensuremath{\mathtt{cext}}}
\newcommand{\rext}{\ensuremath{\mathtt{rext}}}
\newcommand{\cons}{\ensuremath{\mathtt{cons}}}
\newcommand{\decons}{\ensuremath{\mathtt{decons}}}

@@

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings. \lnote{Why limit to authentication}

 This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

A fuzzy extractor performs both these tasks non interactively~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes an initial reading $w$ and produces $key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ should be uniform even if an adversary has observed $p$.  The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.  For any security the initial readings must come from a high min-entropy distribution $W$.

\paragraph{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).  
We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?

\paragraph{Main result}
Our main result is negative~(\thref{thm:imposs sketch}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.   Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.  We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.  Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).

\paragraph{Information-reconciliation in isolation}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  That is, there is a family of distributions for which no secure sketch in possible.  Furthermore, secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}).
\paragraph{Related Settings}
We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  We first consider the interactive setting.  
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is \bnote{what?}

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

@@

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\textbf{Note:} The above result does not rule out a computational secure sketch based on unpredictability~(where $W$ is hard to guess given the string $S$).  Unpredictable secure sketches are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.

@@

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-secure sketch with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).  Obtaining weaker parameters for impossibility of fuzzy extractors makes sense.
\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element in $\mathbb{F}$ and let 
\[w = (x_1,..., x_{\nu})  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

@@

\noindent
\textbf{Note:} Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.  Their construction does not contradict our result because the construction is computationally secure.  (Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)

\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:universal hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

>>>>

\newcommand{\expinfo}{\ensuremath{\mathcal{E}}}
\newcommand{\ext}{\ensuremath{\mathtt{ext}}}
\newcommand{\cext}{\ensuremath{\mathtt{cext}}}
\newcommand{\rext}{\ensuremath{\mathtt{rext}}}
\newcommand{\cons}{\ensuremath{\mathtt{cons}}}
\newcommand{\decons}{\ensuremath{\mathtt{decons}}}
\newcommand{\sd}{\ensuremath{\mathbf{SD}}}

@@

\newpage
\tableofcontents\newpage

\section{Introduction}
Sources of reproducible secret random bits are necessary for many cryptographic applications.  In many situations, these bits are not explicitly stored for future use, but are obtained by repeating the same process  (such as reading a biometric or a physically unclonable function) that generated them the first time.
However, bits obtained this way present a problem: noise \cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when a secret is read multiple times, readings are close~(according to some metric) but not identical.  To utilize such sources it is often necessary to remove noise, in order to derive the same value in subsequent readings.

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

The non interactive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  
A fuzzy extractor consists of two algorithms. The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced if the distance between $w$ and $w'$ is at most $t$.

The security requirement for fuzzy extractors that is $\key$ uniform even to an adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.

Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.  Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.  However, the lower bound is too imprecise (sometimes even negative) for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{Characterization  for Distribution-aware Extractability}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution rather than relying on cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.
It is important to note that this characterization requires the fuzzy extractor to be designed with $W$ in mind. We call such fuzzy extractors \emph{distribution aware}.

\anote{Suggested title: "Impossibility Results for Distribution-Oblivious Sketches and Extractors". Also, "typically fuzzy extractors cannot be tailored". Also "for a family of sources" $\to$ "to a family of sources".}

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\paragraph{Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.  Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c  l l }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch using precise knowledge of the distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. At a minimum the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.  We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  The value $p$ partitions the metric space into regions that produce a consistent value in $\rep$.  For each of these regions the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it must put most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

 The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.  Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.

Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

@@

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

@@

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
%\begin{definition}[Conditional Hartley Entropy]
%\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
%\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
%For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

@@

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\sd((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\textbf{Note:} Secure sketches that provide computational unpredictability are implied by virtual-grey box obfuscation of proximity functions~\cite{BitanskyCKP14}.  Our impossibility result says nothing about this weaker form of a secure sketch.  We do not that extracting from unpredictability requires a extractor with a reconstruction property~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

@@

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ over $\zo^n$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $V$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.  This family is closely related to the family we constructed in \thref{thm:imposs sketch}.  However, we work over the binary alphabet so the affine lines are ``squished'' to the binary realm.  For convenience we assume that $\nu\in\mathbb{Z}^+$.  We describe a single element $W\in V$. Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_1  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} 
\]
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.

@@

\noindent
\textbf{Note:} As stated in \secref{sec:related settings}, using strong computational assumptions it is possible to avoid this result.  We note that the specific family $\mathcal{V}$, Canetti et al.~\cite[Construction 5.3]{canetti2014key} construct computational fuzzy extractors under weaker assumptions for this family of distributions when $\mathbb{F}$ is large enough.  (Their construction is stated with imperfect correctness but can be made perfect by using a code that corrects $t$ bidirectional errors instead of a code that corrects $t$ unidirectional errors.)

\paragraph{Comparison with \thref{thm:imposs sketch}} The parameters in this result are weaker than those in \thref{thm:imposs sketch}.  The major differences are that the result requires: 1) higher error tolerance $t= \omega(n^{1/2}\log n)$ 2) the fuzzy extractor must have perfect correctness.  Note ruling out a fuzzy extractor also rules out a secure sketch~(as a secure sketch can be transformed to a fuzzy extractor).  
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{Old intros}

\subsection{Ben's text from Wed afternoon, incorporated into the above}

Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).  
We ask:  \emph{is fuzzy min-entropy sufficient for key derivation from noisy sources}?

\paragraph{Main result}
Our main result is negative~(\thref{thm:imposs fuzz ext}) is negative: fuzzy extractors are impossible if the distribution $W$ is unknown.   Fuzzy extractors normally assume partial knowledge of a distribution $W$, assuming it comes from a family of distributions $\mathcal{W}$.  We show a family of distributions $\mathcal{W}$ such that no instantiation can be secure for all elements of $\mathcal{W}$.  Each possibility for the distribution $W$ has fuzzy min-entropy and its points are far apart~(intuitively, this should make the task easier).

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.
\section{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:universal hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.
